Manuscript title

### 2018-12-03 Manuscript/manuscript.Rmd
Add to Abstract-results section

**Methods.** We propose a novel data pre-processing pipeline that addresses those shortcomings. A number of classifier performance metrics were assessed, including the F1 measure and Matthew Correlation Coefficient (MCC), and area under the ROC curve (AUROC).

**Results.** Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries.

>>>>

**Methods.** We propose a novel data pre-processing pipeline that addresses those shortcomings. Lasso and Elastic Net were used for feature selection, coupled with five classifier methods. A number of classifier performance metrics were assessed, including the F1 measure and Matthew Correlation Coefficient (MCC), and area under the ROC curve (AUROC).

**Results.** Data preprocessing (log2-transformation and standardization) improves the performance of classification algorithms and allows for the ability to more accurately predict which genomic features are most associated with TAD boundaries. In contrast to overlap-based association measures, distance between genomic elements appears to be the most predictive measure. Random undersampling strategy addresses the class imbalance problem the most effectively in nearly all settings.
